A sheaf--function dictionary for algebraic tori over non-archimedean local fields

### 2013-08-16 shanghai.tex
Small improvements to Part 2.

We would like to thank Masoud Kamgarpour, Pramod Achar, and Hadi Salmasian
for allowing us to hijack our Research in Teams meeting at BIRS into a discussion of
quasicharacter sheaves.  Their knowledge and help have been invaluable.

@@

Let $K$ be a non-archimedean local field with residue field $\Fq$.
We place no restriction on the characteristic of $K$. 
We write $\OK$ for the ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$. 
For any positive integer $d$, set $A_d\ceq \OK/\pK^d$.
Let $T$ be an algebraic torus over $K$.
We write $\Hom_{< d}(T(K),\EEx)$ for the group of characters of $T(K)$ depth less than $d$ 
and $\Hom_{<\infty}(T(K),\EEx)$ for the group of characters of $T(K)$ of arbitrary finite depth; one might call these quasicharacters of $T(K)$, expanding on \cite{tate:67a}*{2.3}.

@@

\section{The geometrization of characters of tori over local fields} \label{sec:quasichar}

\Clifton{I'm working here, now.}

\begin{definition}
The \emph{Greenberg transform of the N\'eron model of $T$} is the group pro-scheme over $\Fq$ given by
\begin{equation}\label{projlim}
  \cdef{\GN{T}} \ceq \varprojlim_{d\in \ZZ_{>0}} \GN{T}_{d}.
\end{equation}
Let$\QC(\GN{T})$ be the ind-category $\varinjlim_{d\in \ZZ_{>0}} \QC(\GN{T}_d)$;
we refer to objects of $\QC(\GN{T})$ as \emph{quasicharacter sheaves for $T$}.
\end{definition}

@@

>>>>

We would like to thank Masoud Kamgarpour, Pramod Achar, and Hadi Salmasian
for allowing us to hijack much of our Research in Teams meeting at BIRS into a discussion of
quasicharacter sheaves.  Their knowledge and help have been invaluable.

@@

Recall that $\Fq$ is a finite field.
Let $K$ be a non-archimedean local field with residue field $\Fq$.
We place no restriction on the characteristic of $K$. 
We write $\OK$ for the ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$. 
For any positive integer $d$, set $A_d\ceq \OK/\pK^d$.
Let $T$ be an algebraic torus over $K$.
We write $\Hom_{< d}(T(K),\EEx)$ for the group of characters of $T(K)$ depth less than $d$ 
and $\Hom_{<\infty}(T(K),\EEx)$ for the group of characters of $T(K)$ of arbitrary finite depth; one might call these quasicharacters of $T(K)$, expanding on \cite{tate:67a}*{2.3}.

@@

\section{A sheaf-function dictionary for tori over local fields} \label{sec:quasichar}

\Clifton{I'm working here, now.}
If $d\leq d'$, then $\pK^{d'} \hookrightarrow \pK^d$ so there is a canonical surjective ring homomorphism $A_{d'} \to A_{d}$. Set $S = \Spec{\OK}$ and $S_d = \Spec{A_d}$. 
\[
\begin{tikzcd}
S_1 \arrow[hook]{r} 
& S_2 \arrow[hook]{r} \cdots 
& S_d \arrow[hook]{r}  
& S_{d'} \arrow[hook]{r} \cdots 
& S
\end{tikzcd}
\]

 then $\GN{T}_d$ is a closed subgroup of $\GN{T}_{d'}$,
so these smooth commutative group schemes form a directed system.
\[
\begin{tikzcd}
\GN{T}_1 
& \arrow[two heads]{l} \GN{T}_2 
& \arrow[two heads]{l} \cdots 
& \arrow[two heads]{l} \GN{T}_d 
& \arrow[two heads]{l} \GN{T}_{d'} 
& \arrow[two heads]{l} \cdots
\end{tikzcd}
\]

\begin{definition}
The \emph{Greenberg transform of the N\'eron model of $T$} is the group pro-scheme over $\Fq$ given by
\begin{equation}\label{projlim}
  \cdef{\GN{T}} \ceq \varprojlim_{d\in \ZZ_{>0}} \GN{T}_{d}.
\end{equation}
\end{definition}

@@

\begin{definition}
Let$\QC(\GN{T})$ be the ind-category $\varinjlim_{d\in \ZZ_{>0}} \QC(\GN{T}_d)$;
we refer to objects of $\QC(\GN{T})$ as \emph{quasicharacter sheaves for $T$}.
\end{definition}
